Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-20 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Add a raw summary.

% \item Jakob Blomer: The Need for a Versioned Data Analysis Environment

>>>>

\item \textbf{Jakob Blomer: The Need for a Versioned Data Analysis Environment}
%
Large-scale scientific endeavors, such as the discovery of the Higgs
boson at the Large Hadron Collider (LHC), often rely on complex software
stacks.  Having to maintain thousands of dependencies of software
libraries and operating system versions, it turns out that despite
source code availability the setup and the validation of a minimal
usable analysis environment can easily become prohibitively expensive.
There is a substantial gap between merely having access to open source
software and the ability to create a data analysis runtime environment.
 In high-energy physics, very positive experience was made with a
special purpose, open-source, versioning and snapshotting file system
(CernVM-FS), that is used to capture and distribute entire software
stacks.  It provides the instant access to ready-to-run data analysis
environments for the global scientific community as well as for
interested citizens, for instance through the CERN Open Data Portal
(http://opendata.cern.ch). \todo{revise}
